Holomorphic field theories and higher algebra

### 2024-09-26 draft.tex
s 6

@@

\begin{eg}[Holomorphic Chern-Simons theory]
\label{eg: holCS}
\owen{This feels rather convoluted. Can we make it simpler?}
Pick a {\em complex} Lie group $G$, 
and equip its Lie algebra $\fg$ with a complex-linear, $G$-invariant nondegenerate symmetric bilinear form~$\kappa$.
Let $M$ be a three-dimensional \textit{complex} manifold
equipped with a holomorphic volume form $\Omega \in \Omega^{3,0}(M)$; 
in other words, $M$ is a Calabi--Yau manifold.
(This condition is analogous to being an oriented 3-manifold.)
Given a smooth principal $G$-bundle $P \to M$,
there is a moduli space of holomorphic structures on~$P$.
Suppose there exists at least one holomorphic structure $\cP \to M$,
which has an associated Dolbeault operator (or $\dbar$-connection) $\dbar_{\cP}$.
Any other holomorphic bundle structure determines a Dolbeault operator,
but our reference point $\dbar_{\cP}$ provides an isomorphism
\[
{\rm Conn}^\dbar_G(P) \cong \Omega^{0,1}(M, \fg_P),
\]
i.e., we express another $\dbar$-connection as $\dbar_{\cP} + A$ where $A$ is a $(0,1)$-form valued in the adjoint bundle.
The equation of motion is again a Maurer--Cartan equation
\beqn
\dbar_{\cP} A + \frac12 [A,A] = 0 ,
\eeqn
or equivalently the $(0,2)$-term of the curvature vanishes.
This PDE is the Euler--Lagrange equation for the action
\beqn
S_{hCS} (A) = \int_M \Omega \wedge CS(A) 
\eeqn
where $CS(A)$ is exactly as in~\eqref{eqn:CS}.\footnote{Notice that due to the presence of the holomorphic volume form $\Omega$, only the $\dbar A$ component of $\d A$ contributes to the integrand of the action functional, because $\Omega \wedge \partial A$ vanishes.} 
As in the case of Chern-Simons theory, one must quotient by the appropriate group of gauge transformations to obtain the correct moduli space, 
which is here the moduli stack of holomorphic principal $G$-bundles whose underlying smooth structure is given by $P \to M$.
\end{eg}

@@

There is a special class of fermionic theories that is quite interesting.
Let $X$ be a complex $n$-fold where
\begin{itemize}
\item $n \equiv 1 \mod 4$ (i.e., $n=4k+1$ for some $k$) and
\item there is a line bundle $L \to X$ such that $L^{\otimes 2} \cong K_X$,
i.e., $L$ is a square root of the canonical bundle.
\end{itemize}
A field is a section
\[
\psi \in \Omega^{0,2k}(X,\Pi L),
\]
the action functional is
\[ 
\int_X \psi \wedge \dbar \psi,
\]
and the equation of motion is
\[
\dbar \psi = 0.
\]
We suggest to identify solutions that differ by $\dbar$-exact terms.

@@

\owen{I think I got the dimension condition correct. Can you double-check?}

@@

There is a natural generalization of the $\beta\gamma$ system to a $\sigma$ model.
Let $M$ be a complex $d$-manifold and let $N$ be a complex $n$-manifold.
The fields are a pair $(\gamma, \beta)$ where
\[
\gamma \in \Map(M,N) \quad\text{and}\quad \beta \in \Omega^{n,n-1}(M,\gamma^* T^*_N) .
\]
Note that $\dbar \gamma$ lives in $\Omega^{0,1}(M, \gamma^* T_N)$, 
a section of the pullback of the tangent bundle of the target.
The action functional is 
\[
\int_X \beta \wedge \dbar \gamma,
\]
where we use the canonical evaluation pairing between the pullback of the tangent and cotangent bundles of the target.
The equations of motion are
\[
\dbar \gamma = 0 = \dbar \beta,
\]
so that solutions consist of a holomorphic map $\gamma: M \to N$ and a holomorphic section $\beta$ of the pullback tangent bundle.
As usual, we suggest to identify solutions to the equation $\dbar \beta = 0$ that differ by a $\dbar$-exact form.

@@

Let $X$ be a complex manifold of complex dimension~$n$.
Fix a complex Lie group $G$ and an invariant symmetric bilinear form $\langle-,-\rangle$ on its Lie algebra~$\fg$.
Fix a holomorphic principal $G$-bundle $P \to X$.
The fields consist of pairs $(A,B)$ where 
\[
A \in \Omega^{0,1}(X, \fg_P)
\] 
where $\fg_P$ is the adjoint bundle of $P$ and
\beqn
B \in \Omega^{n,n-2}(X, \fg_P^*) ,
\eeqn
where $\fg_P^*$ is the coadjoint bundle of $P$. 
The action functional is 
\beqn
S(A,B) = \int_X \langle B \wedge F_A \rangle
\eeqn
where $F_A$ is the curvature of the connection $A$.
The equations of motion are
\[
F_A^{0,2} = \dbar A + \frac12 [A,A] = 0 \text{ and } \dbar B + [A,B] = 0.
\]
A solution to the first equation provides is a $\dbar$-connection 
\[
\dbar_A = \dbar_P + [A,-]
\]
on the underlying smooth bundle $P\to X$, 
\owen{Am I doing that right? I believe a choice of holomorphic structure on $P$ automatically determines a Dolbeault operator, or $\dbar$-connection.}
and a solution to the second equation is a holomorphic $(n,n-2)$-form-valued section of the coadjoint bundle associated to~$\dbar_A$.
This theory is often called {\em holomorphic BF theory}, due to the integrand of the action functional.

\begin{rmk}
Notice that this action functional resembles the $\beta\gamma$ system, 
with $A$ playing the role of $\gamma$ and $B$ playing the role of $\beta$.
A physicist might also recognize this action functional as a holomorphic analog of topological $BF$ theory. 
\end{rmk}

@@

\begin{rmk}
Holomorphic BF theory exhibits some interesting properties at the quantum level,
at least perturbatively.
For example, in \cite{semichiral} it is shown that on $X = \C^2$ 
the perturbative quantization of holomorphic BF theory is almost a topological field theory. 
More precisely, to first-order in perturbation theory, 
the stress tensor has a divergence-free component that is cohomologically trivial. 
In other words, the quantum theory appears to be ``invariant'' under divergence-free vector fields,
although not all vector fields (as in the case of a TFT).
\owen{Add specific location in text.}
\end{rmk}

@@

There is a higher-dimensional analog of the chiral sector of the scalar field.
Let $X$ be a complex manifold of dimension $2n+1$, i.e., odd.
The fields are the $(n+1,n)$-forms $\alpha \in \Omega^{n+1,n}(X)$ that satisfy the constraint
\beqn
\del \alpha = 0.
\eeqn
(When $n=0$ and $X$ is simply a Riemann surface, 
this constraint is automatic.)
The action functional is the same as~\eqref{eqn:scalar1}.
Generally, this theory is the holomorphic part of a higher-form scalar theory, with action
\beqn
\int_X \|C\|^2 \op{dvol} = \int_X \d C \wedge \star \d C , 
\eeqn
where $C \in \Omega^{2n+1}(X)$.
For more details we refer to~\cite{GRWwzw}.

@@

%In complex dimension $3$ there is a related theory, called Kodaira--Spencer theory, which only consists of the field $\mu$ describing the complex structure in the above example.
Let $X$ be a complex threefold equipped with a Calabi--Yau structure; we denote by $\Omega \in \Omega^{3,hol}(X)$ the holomorphic volume form.
The primary field of Kodaira-Spencer theory is 
\beqn
\mu \in \Omega^{0,1}(X,\T_X),
\eeqn 
a $(0,1)$-form  on $X$ with values in the holomorphic tangent bundle~$\T_X$.
In contrast to examples above, a constraint is imposed on these sections:
we assume that $\mu$ preserve the holomorphic volume form $\Omega$, meaning 
\[
{\rm div}_\Omega(\mu) = 0,
\]
i.e., its divergence vanishes.
In short, the fields are divergence-free vector fields.
The equation of motion is 
\beqn
\dbar \mu + \frac12 [\mu,\mu]_{SN} = 0 ,
\eeqn
where $[-,-]_{SN}$ denotes here the Schouten--Nijenhuis bracket.\footnote{On vector fields, $[-,-]_{SN}$ is simply the Lie bracket, and it is the natural multilinear extension to polyvector fields.}
The reader might recognize this equation as the Maurer--Cartan equation controlling deformations of complex structure $\dbar\rightsquigarrow \dbar + \mu$.
Formulating the action functional to obtain this equation of motion is a little involved, 
and we refer to \cite{CLbcov1} for a systematic discussion.

\begin{rmk}
The kinetic term has the form
\[
\int_X \frac12 \mu\, \dbar \del^{-1} \mu
\]
and hence resembles the chiral sector of the scalar, which we just discussed in the preceding example.
\end{rmk}

@@

In this example the PDE arises from the variations of the action functional
\[
\int_X \Omega \wedge \left( \frac{1}{2}\langle A, \dbar A\rangle + \frac{1}{3!}\langle A, [A,A]\rangle \right).
\]
The PDE does not involve the choice of a holomorphic volume form $\Omega$ or a pairing on the Lie algebra $\fg$, 
but the action functional did.

@@

\begin{dfn}
A {\em local cyclic structure} on a holomorphic local Lie algebra is a degree $-3$ map
\[
\langle -,-\rangle: V \otimes V \to K_X
\]
of holomorphic vector bundles\footnote{Here $\otimes$ denotes the Whitney tensor product of vector bundles on $X$.} such that 
\begin{itemize}
\item if $f, g$ are holomorphic sections of $V$, then 
\[
\langle Q^{hol}f, g \rangle + (-1)^{|f|} \langle f, Q^{hol} g \rangle = 0
\]
so that the pairing is a cochain map, and
\item if $f, g, h$ are holomorphic sections of $V$, then 
\[
\langle f, [g,h] \rangle = (-1)^{|f|} \langle h,  \rangle
\]
so that the pairing is invariant for the bracket.
\end{itemize}
\owen{We must check the signs. And am I missing anything?}
\end{dfn}

@@

\owen{What else to say?}

@@

There are many other appearances of holomorphic field theories in the context of supersymmetry.
Here is a (very) non-exhaustive list:
\begin{itemize}
\item Topological string theories yield rich classes of holomorphic field theories, as target space field theories. 
For instance, the topological B-model on a Calabi--Yau threefold $X$ leads to Kodaira--Spencer theory on $X$, as proposed in \cite{BCOV} using the framework of closed string field theory. 
The perspective of Kodaira--Spencer theory as a holomorphic field theory has been explored with great success by Kevin Costello and Si Li \cite{CL1, CL2, CL3}.
\item
It is possible to make sense of Kodaira--Spencer theory outside of three dimensions.
In \cite{CLsugra}, Costello and Li have argued for conjectural descriptions of twists of supergravity and superstring theories in terms of this more general version of Kodaira--Spencer theory.
\item The pure spinor formalism of Berkovits and Cederwall  \cite{Cederwall, Berkovits} starts with a field theory or string theory defined on the (sometimes singular) nilpotence variety of the super Poincar\'e algebra and then uses the action of supersymmetry to produce ordinary (non-twisted) supersymmetric field theories. 
Often, the theory on the nilpotence variety is holomorphic \cite{ESW,SWpure}. 
\item Similar in spirit to the pure spinor formalism is a systematic relationship between holomorphic field theories on (super) twistor space and ordinary (Riemannian) field theories.
For instance, holomorphic BF theory on (super) twistor space associated to $\RR^4$ is equivalent to a self-dual limit of (super) Yang--Mills theory \cite{Penrose, Kevins work..., other twistor literature}.
\end{itemize}
We recommend \owen{is there some other place to point?} for more discussion.

@@

\owen{It would be good to explain why and indicate what is the appropriate "value" to use.}

@@

>>>>

%%% TIKZ STUFF
\usepackage{tikz,tikz-cd}
\usetikzlibrary{arrows,shapes}
\usetikzlibrary{trees}
\usetikzlibrary{matrix,arrows}
\usetikzlibrary{positioning}
\usetikzlibrary{calc,through}
\usetikzlibrary{decorations.pathreplacing}
\usepackage{pgffor}

%%Feynman diagrams
\usetikzlibrary{decorations.pathmorphing}
\usetikzlibrary{decorations.markings}
\tikzset{
	% >=stealth', %%  Uncomment for more conventional arrows
    vector/.style={decorate, decoration={snake}, draw},
	provector/.style={decorate, decoration={snake,amplitude=2.5pt}, draw},
	antivector/.style={decorate, decoration={snake,amplitude=-2.5pt}, draw},
    fermion/.style={draw=black, postaction={decorate},
        decoration={markings,mark=at position .55 with {\arrow[draw=black]{>}}}},
    fermionbar/.style={draw=black, postaction={decorate},
        decoration={markings,mark=at position .55 with {\arrow[draw=black]{<}}}},
    fermionnoarrow/.style={draw=black},
    gluon/.style={decorate, draw=black,
        decoration={coil,amplitude=4pt, segment length=5pt}},
    scalar/.style={dashed,draw=black, postaction={decorate},
        decoration={markings,mark=at position .55 with {\arrow[draw=black]{>}}}},
    scalarbar/.style={dashed,draw=black, postaction={decorate},
        dwecoration={markings,mark=at position .55 with {\arrow[draw=black]{<}}}},
    scalarnoarrow/.style={dashed,draw=black},
    electron/.style={draw=black, postaction={decorate}/,
        decoration={markings,mark=at position .55 with {\arrow[draw=black]{>}}}},
	bigvector/.style={decorate, decoration={snake,amplitude=4pt}, draw},
}

@@

\begin{eg}[Holomorphic Chern-Simons theory]
\label{eg: holCS}
Pick a {\em complex} Lie group $G$, 
and equip its Lie algebra $\fg$ with a complex-linear, $G$-invariant nondegenerate symmetric bilinear form~$\kappa$.
Let $M$ be a three-dimensional \textit{complex} manifold
equipped with a holomorphic volume form $\Omega \in \Omega^{3,0}(M)$; 
in other words, $M$ is a Calabi--Yau manifold.
(This condition is analogous to being an \textit{oriented} 3-manifold.)
Given a smooth principal $G$-bundle $P \to M$,
there is a moduli space of holomorphic structures on~$P$.
Suppose there exists at least one holomorphic structure $\cP \to M$,
which has an associated Dolbeault operator (or $\dbar$-connection) $\dbar_{\cP}$.
Any other holomorphic bundle structure determines a Dolbeault operator,
but our reference point $\dbar_{\cP}$ provides an isomorphism
\[
{\rm Conn}^\dbar_G(P) \cong \Omega^{0,1}(M, \fg_P),
\]
i.e., we express another $\dbar$-connection as $\dbar_{\cP} + A$ where $A$ is a $(0,1)$-form valued in the adjoint bundle.
The equation of motion is again a Maurer--Cartan equation
\beqn
\dbar_{\cP} A + \frac12 [A,A] = 0 ,
\eeqn
or equivalently the $(0,2)$-term of the curvature vanishes.
This PDE is the Euler--Lagrange equation for the action
\beqn
S_{hCS} (A) = \int_M \Omega \wedge CS(A) 
\eeqn
where $CS(A)$ is exactly as in~\eqref{eqn:CS}.\footnote{Notice that due to the presence of the holomorphic volume form $\Omega$, only the $\dbar A$ component of $\d A$ contributes to the integrand of the action functional, because $\Omega \wedge \partial A$ vanishes.} 
As in the case of Chern-Simons theory, one must quotient by the appropriate group of gauge transformations to obtain the correct moduli space, 
which is here the moduli stack of holomorphic principal $G$-bundles whose underlying smooth structure is given by $P \to M$.
\end{eg}

@@

There is another class of fermionic theories that is quite interesting as they are more fundamental than the previous example.
Let $X$ be a complex $n$-fold and $L \to X$ a line bundle on $X$ such that
\begin{itemize}
\item $n \equiv 1 \mod 4$ (i.e., $n=4k+1$ for some $k$) and
\item $L$ is a square root of the canonical bundle $L^{\otimes 2} \cong K_X$.
\end{itemize}
A field is a section
\[
\psi \in \Omega^{0,2k}(X,\Pi L),
\]
and the action functional is
\[ 
\int_X \psi \wedge \dbar \psi .
\]
The equation of motion for this system is simply $\dbar \psi = 0$.
To study the quantization of this system, it is necessary to identify solutions that differ by $\dbar$-exact terms (and identifying identifications that differ by $\dbar$-exact terms, etc.).

@@

@@

There is a natural generalization of the $\beta\gamma$ system to a $\sigma$-model.
Let $M$ be a complex $d$-manifold and let $N$ be a complex $n$-manifold.
The fields are a pair $(\gamma, \beta)$ where
\[
\gamma \in \Map(M,N) \quad\text{and}\quad \beta \in \Omega^{n,n-1}(M,\gamma^* T^*_N) .
\]
Note that $\dbar \gamma$ lives in $\Omega^{0,1}(M, \gamma^* T_N)$, 
a section of the pullback of the tangent bundle of the target.
The action functional is 
\[
\int_X \beta \wedge \dbar \gamma,
\]
where we use the canonical evaluation pairing between the pullback of the tangent and cotangent bundles of the target.
The equations of motion are
\[
\dbar \gamma = 0 = \dbar \beta,
\]
so that solutions consist of a holomorphic map $\gamma: M \to N$ and a holomorphic section $\beta$ of the pullback tangent bundle.
As usual, we suggest to identify solutions to the equation $\dbar \beta = 0$ that differ by a $\dbar$-exact form.

@@

Let $X$ be a complex manifold of complex dimension~$n$.
Fix a complex Lie group $G$ and an invariant symmetric bilinear form $\langle-,-\rangle$ on its Lie algebra~$\fg$.
Fix a holomorphic principal $G$-bundle $P \to X$.
The fields consist of pairs $(A,B)$ where 
\[
A \in \Omega^{0,1}(X, \fg_P)
\] 
where $\fg_P$ is the adjoint bundle of $P$ and
\beqn
B \in \Omega^{n,n-2}(X, \fg_P^*) ,
\eeqn
where $\fg_P^*$ is the coadjoint bundle of $P$. 
The action functional is 
\beqn
S(A,B) = \int_X \langle B \wedge F_A \rangle
\eeqn
where $F_A$ is the curvature of the connection $A$.
The equations of motion are
\begin{align*}
F_A^{0,2} = \dbar A + \frac12 [A,A] & = 0 \\
 \dbar B + [A,B] & = 0.
\end{align*}
A solution to the first equation provides a new $\dbar$-connection 
\[
\dbar_A = \dbar_P + [A,-] 
\]
on $P$.
A solution to the second equation is a $\dbar_A$-flat $(n,n-2)$-form-valued section of the coadjoint bundle.
This theory is often called {\em holomorphic BF theory}, due to the integrand of the action functional.

\begin{rmk}
Notice that this action functional resembles the $\beta\gamma$ system, 
with $A$ playing the role of $\gamma$ and $B$ playing the role of $\beta$.
One also recognizes this action functional as a holomorphic analog of topological $BF$ theory. 
\end{rmk}

@@

\begin{rmk}
Holomorphic BF theory exhibits some interesting properties at the quantum level,
at least perturbatively.
For example, in \cite[\S3.2]{semichiral} it is shown that on $X = \C^2$ 
the perturbative quantization of holomorphic BF theory is almost a topological field theory. 
More precisely, to first-order in perturbation theory, 
the divergence-free component of the stress tensor is rendered cohomologically trivial at one-loop in perturbation theory.
In other words, the quantum theory appears to be totally ``invariant'' under divergence-free vector fields,
although not all vector fields (as in the case of a TFT).
\end{rmk}

@@

There is a higher-dimensional analog of the chiral sector of the scalar field.
Let $X$ be a complex manifold of dimension $2n+1$, i.e., odd.
The fields are the $(n+1,n)$-forms $\alpha \in \Omega^{n+1,n}(X)$ that satisfy the constraint
\beqn
\del \alpha = 0.
\eeqn
(When $n=0$ and $X$ is simply a Riemann surface, 
this constraint is automatic.)
The action functional is $\int_X \alpha \dbar(\del^{-1} \alpha)$, the same as~\eqref{eqn:scalar1}.
Generally, this theory is the holomorphic part of a higher-form scalar theory, with action
\beqn
\int_X \|C\|^2 \op{dvol} = \int_X \d C \wedge \star \d C , 
\eeqn
where $C \in \Omega^{2n+1}(X)$.
For more details we refer to~\cite{GRWwzw}.

The reader may (and should) be concerned with the apparent `non-local' form of the action functional in \eqref{eqn:scalar1}.
This can be made rigorous by cohomologically resolving the condition that $\alpha$ be $\del$-closed, rather than strictly imposing the constraint \cite{CLbcov1}.

@@

%In complex dimension $3$ there is a related theory, called Kodaira--Spencer theory, which only consists of the field $\mu$ describing the complex structure in the above example.
Let $X$ be a complex threefold equipped with a Calabi--Yau structure; we denote by $\Omega$ the holomorphic volume form.
The primary field of Kodaira-Spencer theory is 
\beqn
\mu \in \Omega^{0,1}(X,\T_X),
\eeqn 
a $(0,1)$-form  on $X$ with values in the holomorphic tangent bundle~$\T_X$.
A constraint is imposed on these sections:
we assume that $\mu$ preserve the holomorphic volume form $\Omega$, meaning 
\[
{\rm div}_\Omega(\mu) = 0,
\]
i.e., its divergence vanishes.
In short, the fields are divergence-free vector fields.
The classical equation of motion is 
\beqn
\dbar \mu + \frac12 [\mu,\mu]_{SN} = 0 ,
\eeqn
where $[-,-]_{SN}$ denotes here the Schouten--Nijenhuis bracket.\footnote{On vector fields, $[-,-]_{SN}$ is simply the Lie bracket, and it is the natural multilinear extension to polyvector fields.}
The reader might recognize this equation as the Maurer--Cartan equation controlling deformations of complex structure $\dbar\rightsquigarrow \dbar + \mu$.
Formulating the action functional to obtain this equation of motion is a little involved, 
and we refer to \cite{CLbcov1} for a systematic discussion.

\begin{rmk}
The kinetic term of this theory has the form
\[
\int_X \Omega \wedge \left[\Omega \vee \left(\frac12 \mu\, \dbar \del^{-1} \mu\right) \right]
\]
and hence resembles the chiral sector of the scalar, which we just discussed in the preceding example.
\end{rmk}

@@

In this example the PDE arises from the variations of the action functional
\[
\int_X \Omega \wedge \left( \frac{1}{2}\langle A, \dbar A\rangle + \frac{1}{3!}\langle A, [A,A]\rangle \right).
\]
The PDE does not involve the choice of a holomorphic volume form $\Omega$ or a pairing on the Lie algebra $\fg$, 
but the action functional does.

@@

\begin{dfn}
A {\em local cyclic structure} on a holomorphic local Lie algebra is a degree $-3$ map
\[
\langle -,-\rangle \colon V \otimes V \to K_X
\]
of holomorphic vector bundles\footnote{Here $\otimes$ denotes the Whitney tensor product of vector bundles on $X$.} such that 
\begin{itemize}
\item if $f, g$ are holomorphic sections of $V$, then 
\[
\langle Q^{hol}f, g \rangle + (-1)^{|f|} \langle f, Q^{hol} g \rangle = 0
\]
so that the pairing is a cochain map, and
\item if $f, g, h$ are holomorphic sections of $V$, then 
\[
\langle f, [g,h] \rangle = (-1)^{|f|} \langle [g,f],h \rangle
\]
so that the pairing is invariant for the bracket.
\end{itemize}
\end{dfn}

@@

@@

There are many other appearances of holomorphic field theories in the context of supersymmetry.
Here is a (very) non-exhaustive list:
\begin{itemize}
\item Topological string theories yield rich classes of holomorphic field theories, as target space field theories. 
For instance, the topological B-model on a Calabi--Yau threefold $X$ leads to Kodaira--Spencer theory on $X$, as proposed in \cite{BCOV} using the framework of closed string field theory. 
The perspective of Kodaira--Spencer theory as a holomorphic field theory has been explored with great success by Kevin Costello and Si Li \cite{CL1, CL2, CL3}.
\item
It is possible to make sense of Kodaira--Spencer theory outside of three dimensions.
In \cite{CLsugra}, Costello and Li have argued for conjectural descriptions of twists of supergravity and superstring theories in terms of this more general version of Kodaira--Spencer theory.
\item The pure spinor formalism of Berkovits and Cederwall  \cite{Cederwall, Berkovits} starts with a field theory or string theory defined on the (sometimes singular) nilpotence variety of the super Poincar\'e algebra and then uses the action of supersymmetry to produce ordinary (non-twisted) supersymmetric field theories. 
Often, the theory on the nilpotence variety is holomorphic \cite{ESW,SWpure}. 
\item Similar in spirit to the pure spinor formalism is a systematic relationship between holomorphic field theories on (super) twistor space and ordinary (Riemannian) field theories.
For instance, the Penrose corresponds relates holomorphic BF theory on (super) twistor space associated to $\RR^4$ to the self-dual limit of (super) Yang--Mills theory \cite{Penrose, Kevins work..., other twistor literature}.
\end{itemize}
We recommend \owen{is there some other place to point?} for more discussion.

@@

\owen{It would be good to explain why and indicate what is the appropriate "value" to use.}
\brian{What?}

@@

As an example, consider holomorphic BF theory on $\C^2$, for some Lie algebra $\lie{g}$, coupled to the $\beta\gamma$ system on $\C^2$ valued in a representation $V$ of $\lie{g}$.
There are two diagrams which contribute to the gauge anomaly, all of which come from various ways of labeling the vertices and edges of the wheel diagram with three vertices, see figure \ref{??}:
\begin{itemize}
\item The pure gauge anomaly.
This part of the anomaly is proportional to the representation theoretic factor $\op{Tr}_{ad}(X^3)$, $X \in \lie{g}$.
This vanishes when $\lie{g}$ is simple, for example, when $\lie{g} = \lie{sl}(n)$).
\item This anomaly involves edges (propagators) labeled by the $\beta\gamma$ fields.
This part of the anomaly is proportional to the representation theoretic factor $\op{Tr}_V(X^3)$, $X \in \lie{g}$.
\end{itemize}
These anomalies in complex two-dimensional holomorphic gauge theory are holomorphic avatars of the Adler--Bell--Jackiw, or chiral, anomaly in ordinary gauge theory \cite{??}.
In the case that $\lie{g}$ is simple (so that the first diagram does not contribute to the anomaly) we see an easy method to produce a non-anomalous holomorphic QFT: take $V$ to be a symplectic representation of the gauge Lie algebra $V = Q \oplus Q^*$, where $Q$ is any $\lie{g}$-representation.

\begin{figure}
\begin{center}
\begin{tikzpicture}
	\begin{scope}
%\pgfmathsetmacro{\ex}{0 }
%\pgfmathsetmacro{\ey}{1}

%\draw (\ex,\ey) ++(45:.8) arc (45:-45:.8);

		\coordinate (O) at (0,0);
		\node[draw] (ci) at (O) [circle through=(right:1)] {};
		%\draw[fill=black] (0,0) circle (1cm);
		%\draw[fill=white] (0,0) circle (0.99cm);
		%\draw[line width=0.35mm,red] ++(145:0.995) arc (145:215:0.995);
		%\node[red] at (180:0.7) {$K_\epsilon$};
		\draw[fermion](45:2) -- (45:1);
		\draw[fermion](180:2) -- (180:1);
		\draw[fermion](315:2) -- (315:1);
		\node at (45:2.2) {$A$};
		\node at (180:2.2) {$A$};
		\node at (315:2.2) {$A$};
		\node at (130:1.4) {$P_{BF}$};
		\node at (270:1.4) {$P_{BF}$};
		\node at (0:1.4) {$P_{BF}$};
	    	\clip (0,0) circle (1cm);
		\end{scope}

		\begin{scope}[shift={(6,0)}]
				\coordinate (O) at (0,0);
		\node[draw] (ci) at (O) [circle through=(right:1)] {};
		%\draw[fill=black] (0,0) circle (1cm);
		%\draw[fill=white] (0,0) circle (0.99cm);
		%\draw[line width=0.35mm,red] ++(145:0.995) arc (145:215:0.995);
		%\node[red] at (180:0.7) {$K_\epsilon$};
		\draw[fermion](45:2) -- (45:1);
		\draw[fermion](180:2) -- (180:1);
		\draw[fermion](315:2) -- (315:1);
		\node at (45:2.2) {$A$};
		\node at (180:2.2) {$A$};
		\node at (315:2.2) {$A$};
		\node at (130:1.4) {$P_{\beta\gamma}$};
		\node at (270:1.4) {$P_{\beta\gamma}$};
		\node at (0:1.4) {$P_{\beta\gamma}$};
	    	\clip (0,0) circle (1cm);
 \end{scope}
\end{tikzpicture}
\caption{Diagrams which contribute to the anomaly in holomorphic gauge theory on $\C^2$}
\label{fig:localization}
\end{center}
\end{figure}
